Structural analysis

### 2025-03-24 workflow/notebooks/draft.Rmd

unrooted_trees <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/trees/", 
                              params_dataset$seed, "_unrooted_trees.txt")
unrooted_trees <- "test/flashforward/out/unrooted_trees.txt"

disco_folder <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/disco")
disco_folder <- "test/flashforward/reco/"

notung <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/", 
                              params_dataset$seed, "_notung.tsv")
notung <- "test/flashforward/out/notung.txt"

apro_folder <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/apro")
apro_folder <- "test/flashforward/reco/"

@@

# ML trees with selected model and LL
mltrees <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/trees/", 
                              params_dataset$seed, "_mltrees.txt")
mltrees <- "test/flashforward/out/mltrees.txt"

@@

disco_fls <- list.files(disco_folder, 
                        pattern = "*output*", full.names = T)
disco_fls <- list.files(disco_folder, 
                        pattern = "^disco", full.names = T)

@@

apro_files <- list.files(apro_folder, 
                        pattern = "*support.nwk", full.names = TRUE)
apro_files <- list.files(apro_folder, 
                        pattern = "^apro", full.names = TRUE)

@@

save.image(file = "workflow/notebooks/eda_cache/until_dftree.Rdata")
```

@@

disco_files_ft <- list.files(bench_dir, pattern = "^disco", full.names = T)
disco_rf_ft <- get_disco_rf(disco_files_ft, sptree_ft) %>% 
  mutate(mat = gsub(".txt", "", targets)) %>% 
  select(-targets, -alphabet, -model)

@@

left_side <- ((apro_plot_ft | disco_plot_ft) / (notung_plot_ft | TCS_plot))
fig_S3 <- (left_side | TCS_scatter) +
  plot_layout(widths = c(1,1)) +
  plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 10, face = "bold", family = "Helvetica"))

ggsave("draft/figures/Fig_S3.pdf", fig_S3, width = 11, height = 5, device = cairo_pdf)
```

>>>>

unrooted_trees <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/trees/", 
                              params_dataset$seed, "_unrooted_trees.txt")
# unrooted_trees <- "test/flashforward/out/unrooted_trees.txt"

disco_folder <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/disco")
# disco_folder <- "test/flashforward/reco/"

notung <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/", 
                              params_dataset$seed, "_notung.tsv")
# notung <- "test/flashforward/out/notung.txt"

apro_folder <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/apro")
# apro_folder <- "test/flashforward/reco/"

@@

# ML trees with selected model and LL
mltrees <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/trees/", 
                              params_dataset$seed, "_mltrees.txt")
# mltrees <- "test/flashforward/out/mltrees.txt"

@@

disco_fls <- list.files(disco_folder, 
                        pattern = "*output*", full.names = T)
# disco_fls <- list.files(disco_folder, 
#                         pattern = "^disco", full.names = T)

@@

apro_files <- list.files(apro_folder, 
                        pattern = "*support.nwk", full.names = TRUE)
# apro_files <- list.files(apro_folder, 
#                         pattern = "^apro", full.names = TRUE)

@@

# save.image(file = "workflow/notebooks/eda_cache/until_dftree.Rdata")
```

@@

disco_files_ft <- list.files(bench_dir, pattern = "^disco", full.names = T)
disco_rf_ft <- get_disco_rf_ft(disco_files_ft, sptree_ft) %>% 
  mutate(mat = gsub(".txt", "", targets)) %>% 
  select(-targets, -alphabet, -model)

@@

left_side <- ((apro_plot_ft | disco_plot_ft) / (notung_plot_ft | TCS_plot))
fig_S3 <- (left_side | TCS_scatter) +
  plot_layout(widths = c(1.2,1)) +
  plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 10, face = "bold", family = "Helvetica"))

ggsave("draft/figures/Fig_S3.pdf", fig_S3, width = 11.5, height = 5, device = cairo_pdf)
```
